### 2024-06-24 manuscript.tex
Improve example figure

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/example.png}
\caption{
An example of attenuated volume backscattering coefficient (AVBC) measured by
CL51 during 24 hours on the PS81/3 voyage and an equivalent AVBC simulated with
the ALCF from ERA5 data during the same time period. Shown is also the cloud
mask determined by the ALCF.
}
\label{fig:example}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/example.png}
\caption{
An example of attenuated volume backscattering coefficient (AVBC) \textbf{(a)}
measured by CL51 during 24 hours on the PS81/3 voyage and \textbf{(b)} an
equivalent AVBC simulated with the ALCF from ERA5 data during the same time
period. Shown is also the cloud mask determined by the ALCF.
}
\label{fig:example}
\end{figure}
